Examining the impact Overturn of Roe v. Wade: Banning of Abortion on Infant Mortality Rates in the United States Using a Difference-in-Differences Approach

### 2024-11-28 paper/ExaminingtheimpactOverturnofRoev.Wade:BanningofAbortiononInfantMortalityRatesintheUnitedStatesUsingaDifference-in-DifferencesApproach.qmd
update pdf of paper

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
set.seed(123)

# Split the data into training and testing sets (80/20 split)
train_index <- createDataPartition(analysis_data$death_rate, p = 0.8, list = FALSE)
train_data <- analysis_data[train_index, ]
test_data <- analysis_data[-train_index, ]

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
# Fit a Bayesian model on the training set
model2 <- stan_glmer(
  death_rate ~ after_injunction * abortion_illegal + year_of_death + age_of_mother + mothers_single_race + (1 | state),
  data = train_data,
  family = gaussian(),
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 2.5),
  prior_aux = exponential(1),
  iter = 2000, chains = 4, seed = 123
)
# Make predictions on the test set
predictions <- posterior_predict(model2, newdata = test_data)
predicted_means <- rowMeans(predictions)  # Average over posterior samples

>>>>

```{r}
#| echo: false
#| eval: false
#| message: false
#| warning: false
#| include: false

set.seed(123)
# Split the data into training and testing sets (80/20 split)
train_index <- createDataPartition(analysis_data$death_rate, p = 0.8, list = FALSE)
train_data <- analysis_data[train_index, ]
test_data <- analysis_data[-train_index, ]

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| include: false

set.seed(123)
train_index <- createDataPartition(analysis_data$death_rate, p = 0.8, list = FALSE)
train_data <- analysis_data[train_index, ]
test_data <- analysis_data[-train_index, ]
model2 <- stan_glmer(
  death_rate ~ after_injunction * abortion_illegal + year_of_death + age_of_mother + mothers_single_race + (1 | state),
  data = train_data,
  family = gaussian(),
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 2.5),
  prior_aux = exponential(1),
  iter = 2000, chains = 4, seed = 123
)
# Make predictions on the test set
predictions <- posterior_predict(model2, newdata = test_data)
predicted_means <- rowMeans(predictions)  # Average over posterior samples
